---
title: "Writing Functions"
subtitle: "a brief introduction"
author: "Andrew Ellis"
date: "`r Sys.Date()`"
output:
  tint::tintHtml: 
     self_contained: TRUE
# bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tint)
# invalidate cache when the package version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tint'))
options(htmltools.dir.version = FALSE)
```


# When should you write a function?

Have you ever done anything like this (the example is from Hadley Wickham's book [Advanced R Programming](http://adv-r.had.co.nz)):


```{r}
# Generate a sample dataset
create_dataframe <- function(na_value = -99) {
    set.seed(1014)
    df <- data.frame(replicate(6, sample(c(1:10, 
                                           na_value), 
                                         6, rep = TRUE)))
    names(df) <- letters[1:6]
    df
}

```

```{r}
df <- create_dataframe()
```

Now, let's replace all those `-99` values with `NA`s:

```{r}
df$a[df$a == -99] <- NA
df$b[df$b == -99] <- NA
df$c[df$c == -98] <- NA
df$d[df$d == -99] <- NA
df$e[df$e == -99] <- NA
df$f[df$g == -99] <- NA
```

Ok, this is painful, and error-prone. We might make copy-paste errors. 

```{marginfigure}
Can anyone spot an error?
```

Let's do the right thing: start again, and write a function:


```{r}
df <- create_dataframe()
df
```



```{r}
fix_missing <- function(x) {
  x[x == -99] <- NA
  x
}
```



Now we can apply the function to each variable in the data frame:

For example:
```{r}
df$d
```
contains one `-99` value.


```{r}
df$a <- fix_missing(df$a)
df$b <- fix_missing(df$b)
df$c <- fix_missing(df$c)
df$d <- fix_missing(df$d)
df$e <- fix_missing(df$e)
df$f <- fix_missing(df$e)
```


This is better, but still involves copying and pasting (should be avoided at all costs). In R, we would do something like this:

```{r}
df <- create_dataframe()
df
```

```{r}
df[] <- lapply(df, fix_missing)
df
```


But what if we have a new dataset with `-98` as a missing value, instead of `-99`? 
```{r}
df <- create_dataframe(na_value = -98)
df
```



Let's write a new function:

```{r}
fix_missing <- function(x, na_value = -99) {
  x[x == na_value] <- NA
  x
}
```

Now we can pass in the correct value as an argument^[When using lapply, arguments to the function being applied are passed as argmuments to `lapply()`.] :

```{r}
df[] <- lapply(df, fix_missing, na_value = -98)
df
```

# How to write a function

There are three key steps to creating a new function:

1) Pick a name for the function. Here we called the function `fix_missing` because that's a fairly accurate description of what is does.

2) List the inputs, or arguments, to the function. Here we have two arguments: `x` and `na_value`

3) Place the code in the body of the function. This is the bit inside the curly braces `{}`. The __return value__ of the function will be the last expression evaluated inside the function. R only returns a single object; if you want more than one object to be returned, you need to place these inside a list.


```
fix_missing <- function(x, na_value = -99) {
  x[x == na_value] <- NA
  x
}
```

The first argument, `x`, does not have a default value, whereas the second argument, `na_value` has a default value of `-99`. Aguments with default values __can be omitted__ when calling the function, argument without default values are __required__.




# Exercise

Now, let's do a little exercise:

- Write a function that computes the $k^{th}$ power of an argument x, using one default argument, and one optional argument, i.e. an argument that has a default value.
- And now extend the function to return both `x^k` and a description (`as.character`) of the function call.





# Solutions

## Basic power function

```{r}
power_fun_1 <- function(x, k = 2) {
    x^k
}
```

```{r}
power_fun_1(3)
```


## Power function that returns a list
```{r}
power_fun_2 <- function(x, k = 2) { 
    list(result = x^k, 
         call = paste(as.character(x), "to the power of", 
                      as.character(k)))
}
```

```{r}
power_fun_2(2, 3)
```


## Power function with a class attribute and plot method

```{r}
power_fun_3 <- function(x, k = 2) { 
    out <- list(result = x^k,
                x = x,
                k = k,
         call = paste(as.character(x), "to the power of", 
                      as.character(k)))
    class(out) <- "some_class"
    out
}
```

```{r}
plot.some_class <- function(z) {
    curve(x^z$k, -2*z$x, 2*z$x, lwd = 3, 
          col = "violet", ylab = z$call,
          xlab = "x")
    points(z$x, z$result, pch = 19, col = "blue", cex = 3)
}
```

```{r fig-margin, fig.margin = TRUE, fig.cap = "Power function plot", fig.width=3.5, fig.height=3.5, cache=TRUE}
out <- power_fun_3(2, k = 3)
plot(out)
```


# Session info
```{r}
sessionInfo()
```

