---
title: "Untitled"
author: "Andrew Ellis"
date: "12/22/2016"
output: 
  html_document: 
    fig_caption: yes
    number_sections: yes
    theme: spacelab
    toc: yes
  word_document: 
    fig_caption: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Markdown

This is an _R_ Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

- item 1
    - nested 1
- item 2

1) numbered 1
2) numbered 2

```{r cars}
summary(cars)
```

## Including Plots

enteer some text here $y \sim N(\mu, \sigma^2)$ and maybe here

You can also embed plots, for example:

```{r echo=TRUE, warning=FALSE}
x <- 35
```
refer to this variable. x has the value `r x`


```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
